### 2025-08-03 machine-learning.qmd
20250803 - shrinkage

@@

@@

>>>>

#### Evaluate Accuracy of Model on Training Data {#sec-treeBoostingModelAccuracyTraining}

```{r}
# Model-implied predictions
pred_train_qb <- predict(
  gp_model_fit_qb,
  data = data_train_qb_matrix[, pred_vars_qb],
  group_data_pred = data_train_qb_matrix[, "gsis_id"],
  group_rand_coef_data_pred = cbind(
    data_train_qb_matrix[, "ageCentered20"],
    data_train_qb_matrix[, "ageCentered20Quadratic"]),
  predict_var = FALSE,
  pred_latent = FALSE)

petersenlab::accuracyOverall(
  predicted = pred_train_qb[["response_mean"]],
  actual = data_train_qb_matrix[, "fantasyPoints_lag"],
  dropUndefined = TRUE
)
```

@@

accuracyIndices_treeBoosting_train <- petersenlab::accuracyOverall(
  predicted = pred_train_qb[["response_mean"]],
  actual = data_train_qb_matrix[, "fantasyPoints_lag"],
  dropUndefined = TRUE
)

rsquare_treeBoosting_train <- round(accuracyIndices_treeBoosting_train$rsquared, digits = 2)

@@

There was moderate [shrinkage](#sec-shrinkage) from the training model to the test model: the $R^2$ for the model on the training data was `{r} rsquare_treeBoosting_train`; the $R^2$ for the same model applied to the test data was `{r} rsquare_treeBoosting`.
